---
title: "Projecting Wins by WAR: A Tutorial"
author: "Erik Larsen"
date: 'June 6th, 2022'
output: github_document
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(fig.show = TRUE)
```

This is a tutorial script for scraping and plotting some baseball data.

## Import Packages

First, import the required packages.

These include [tidyverse](https://cran.r-project.org/package=tidyverse) which provides `SQL` functionality. Super-useful cheat-sheet for it can be found [here](https://nyu-cdsc.github.io/learningr/assets/data-transformation.pdf), and [here](http://www.hcbravo.org/IntroDataSci/classroom-notes/sql_baseball.html) is an additional `tidyverse` example specific to baseball.

[ggplot2](https://cran.r-project.org/package=ggplot2) is the package that enables visualization of those gorgeous graphs.

[rvest](https://cran.r-project.org/package=rvest) allows you to scrape from websites.

[XML](https://cran.r-project.org/package=XML) is similar.

Might eventually need [stringr](https://cran.r-project.org/package=stringr) and [stringi](https://cran.r-project.org/package=stringi) to manipulate strings-- this is useful because when you combine tables of different string encodings (i.e. `Baseball Reference` and `FanGraphs`), the tables won't combine!

Lastly, the [mlbplotR](https://github.com/camdenk/mlbplotR) is awesome. It is a wrapper for `ggplot2` and allows for plotting team colors, logos, player faces, official team nicknames, and cities.

A standard package to use is the [baseballr](https://cran.r-project.org/package=baseballr)

```{r Package Import, include = TRUE, message = FALSE, warning = FALSE, echo = TRUE}
library(tidyverse)
library(ggplot2)
library(rvest)
library(XML)

library(stringr)
library(stringi)
```

If you don't have the [devtools](https://cran.r-project.org/package=devtools) package installed, install it and load it.

You need it to install the [mlbplotR](https://github.com/camdenk/mlbplotR) package from a github account.

```{r mlbplotR install, include = TRUE, message = FALSE, warning = FALSE, echo = TRUE}
  ## Install the mlbplotR pacakge; uncomment the following line to install it.
#devtools::install_github("camdenk/mlbplotR")

  ## Load the package from your library
library(mlbplotR)
```

## Scraping

We need data to plot. I built a model from `Baseball Reference`, scraping `standings` and `bWAR` data from 2011-2021.

I made a couple of scraping functions for these tasks and looped over the years and data types. For example:

```{r BBRef Player Value Scrape (bWAR), include = TRUE, echo = TRUE, warning = FALSE, message = FALSE}
## Scrape all the data from desired seasons
    ## Team player values
ValScrape = function(year){
    ## Scrape hitters
      ## paste the generic part of the html address into the "read_html" function
        ## make the input variable to the function the year that will be plugged
        ## in to the paste function; this will enable read_html to read the whole html address
        
      ## Use tidyverse/SQL functionality to send this output as input to the "html_node" function
        ## I found the selector for this node ("#teams_value_batting") using "Developer Tools"
        ## using my Chrome Browser. You can find how to do this online, or just ask me.
        
      ## Pipe this output into the "html_table" function to create a table from the specific
      ## webpage you just scraped
      
      ## Re-arrange/extract the desired columns from this table by piping the table output into
      ## the "select" function
    
    ## Make this table a variable 
  bat_df = read_html(paste("https://www.baseball-reference.com/leagues/majors/",
                           year,
                           "-value-batting.shtml",
                           sep = "")) %>%
    html_node('#teams_value_batting') %>%
    html_table() %>%
    dplyr::select(Tm, oWAR, dWAR, WAR, Salary)
  
    ## Remove excess rows
  bat_df = bat_df[1:30,]
    ## Add the "Year" column to track years after combining all the dataframes
  bat_df = add_column(bat_df, year = year)
  
    ## Scrape pitchers as above
  pit_df = read_html(paste("https://www.baseball-reference.com/leagues/majors/",
                           year,
                           "-value-pitching.shtml",
                           sep = "")) %>%
    html_node('#teams_value_pitching') %>%
    html_table() %>%
    dplyr::select(Tm, RAA, WAA, WAR, Salary)
  
  pit_df = pit_df[1:30,]
  
  pit_df = add_column(pit_df, year = year)
  
    ## Copy the batting df into a new variable
  df = bat_df
    ## Sum the pitching and hitting WARs for a total
  df$WAR = as.numeric(df$WAR) + as.numeric(pit_df$WAR)
    ## Convert the salary strings to numeric and scale to millions
  df$Salary = as.numeric(
    gsub(df$Salary, pattern = "\\$|\\,", replacement = ""))/1000000
  
    ## Assign each year's dataframe to a variable;
    ## --> Each year is a dataframe of team WAR for all teams;
      ## Looping over a desired year range will fill your global environment
      ## with these variables
  assign(paste("Tot_Val_", year, sep = ""), df, envir = .GlobalEnv)
}
```

Loop over the years we want with the function we just created to make/get dataframes of team `WAR` values.
The model we'll build is from my article on [TheLeftyCatcher](https://www.theleftycatcher.com/post/diving-deep-into-tanking)- based off of 2011-2021 data. That data won't be visualized here.

```{r Looping over years for WAR values, include = TRUE, echo = TRUE, warning = FALSE, message = FALSE}
for(i in 2011:2023){
  
  if (i %% 10 == 0 ){
    
    Sys.sleep(60)
    
    } else {
      
     ValScrape(year = i) 
      
    }
}
    ## Put all together
      ## "reduce" will compact dataframes/variables of the same structure
      ## "mget" will find variables
        ## I took any variables from the global environment ("ls()")
        ## with the pattern, " 'Tot_Val' ". I used 'full_join' as the method by which to
        ## join all the dataframes; this keeps all columns
Tot_Val_All = purrr::reduce(mget(ls()[which(grepl(ls(), pattern = "Tot_Val") == TRUE)]), full_join)

  ## Streamline team names (Marlins, Guardians, Angels); re-name "Tm" strings so that they are the same
  ## across dataframes
Tot_Val_All$Tm[ which(Tot_Val_All$Tm == "Cleveland Indians")] = "Cleveland Guardians"
Tot_Val_All$Tm[ which(grepl(Tot_Val_All$Tm, pattern = "Marlins") == TRUE) ] = "Miami Marlins"
Tot_Val_All$Tm[ which(grepl(Tot_Val_All$Tm, pattern = "Angels") == TRUE) ] = "Los Angeles Angels"

Tot_Val_All = Tot_Val_All %>%
  dplyr::filter(year != 2020)
```

Repeat the same process, but for `standings`.

This is a bit different because there are multiple tables on the same webpage. So, the creators buried the later
tables as comments to fold in the data.

It took a long time for me to figure out a work-around.

```{r Create the Standings Scraping Function, include = TRUE, echo = TRUE, warning = FALSE, message = FALSE}
    ## Scrape team standings
StandScrape = function(year){
  df = read_html(paste("https://www.baseball-reference.com/leagues/majors/",
                       year,
                       "-standings.shtml",
                       sep = "")) %>%
    ## Find commented nodes
    html_nodes(xpath = '//comment()') %>%
    ## Pipe them "html_text" to convert to text
    html_text() %>%
    ## Remove spaces and pipe into "read_html"
    paste(collapse = '') %>%
    read_html() %>%
    ## Find the expanded standings node
      ## This hashtag can be found by exploring with "Developer Tools" on your webbrowser
    html_node('#expanded_standings_overall') %>%
    ## Pipe this node to "html_table" to create a table from the specific webpage destination
    html_table()
  
  ## Remove Rank column and the average row
  df = df[-31,-1]
  
  ## Add Games col
  df = add_column(df, G = df$W + df$L, .before = 2)
  
  ## Add Year col
  df = add_column(df, year = year)
  
  
  assign(paste("Tot_Stand_", year, sep = ""), df, envir = .GlobalEnv)
}
```

Run the function and loop over it. Fix team name strings to be uniform throughout the variable.

```{r Scrape the Standings data by looping over the function within a desired length of time, include = TRUE, echo = TRUE, message = FALSE, warning = FALSE}
  ## Loop over the desired years
for(i in 2011:2023){
  
  if (i %% 10 == 0) {
  
      Sys.sleep(60)
  
    } else {
      
      StandScrape(year = i) 
  }
}

    ## Put all together, as with WAR data
Tot_Stand_All = purrr::reduce(mget(ls()[which(grepl(ls(), pattern = "Tot_Stand") == TRUE)]), full_join)

## Streamline team names (Marlins, Guardians, Angels
Tot_Stand_All$Tm[ which(Tot_Stand_All$Tm == "Cleveland Indians")] = "Cleveland Guardians"
Tot_Stand_All$Tm[ which(grepl(Tot_Stand_All$Tm, pattern = "Marlins") == TRUE) ] = "Miami Marlins"
Tot_Stand_All$Tm[ which(grepl(Tot_Stand_All$Tm, pattern = "Angels") == TRUE) ] = "Los Angeles Angels"
```

Re-arrange the compiled dataframes so that they both can be merged into one object.
Object will be useful for plotting

```{r Combine WAR and Standings data, include = TRUE, echo = TRUE, warning = FALSE, message = FALSE}
  ## Re-arrange in alphabetical order
Tot_Val_All = Tot_Val_All %>%
  arrange(Tm)

Tot_Stand_All = Tot_Stand_All %>%
  arrange(Tm)

    ## Add G, WAR/G, Ws, W%s
    
  ## Co-erce the data types to be "numeric" to enable mathematic operations
Tot_Val_All$G = as.numeric(Tot_Stand_All$G)
  ## Create the WAR / G variable
Tot_Val_All$WARPG = as.numeric(Tot_Val_All$WAR) / as.numeric(Tot_Stand_All$G)

Tot_Val_All$W = as.numeric(Tot_Stand_All$W)
Tot_Val_All$W_L = as.numeric(Tot_Stand_All$`W-L%`)

```

## Build a Regresssion Model

Use R's `lm` function to build a linear regression model from `Tot_Val_All_sub` that contains `bWAR` and `Standings` data.

Use `WARPG` (`WAR` / `G`) as a predictor (independent/X-axis variable) for `W%` (`W_L`).

```{r include = TRUE, echo = TRUE, warning = FALSE, message = FALSE}
  ## W% ~ WAR (all)
WL_WARPG_lm = lm(data = Tot_Val_All, formula = W_L~WARPG)
  ## Inspect by seeing the model's coefficient of determination
summary(WL_WARPG_lm)$r.squared
  ## Print some of the coefficients for plotting (intercept in this case)
as.numeric(coefficients(WL_WARPG_lm)[1])

  ## RMSE
# sqrt(mean((Tot_Val_All$W_L - as.numeric(WL_WARPG_lm$fitted.values))^2))
```

```{r include = TRUE, echo = FALSE, warning = FALSE, message = FALSE}
WL_WAR_lm = lm(data = Tot_Val_All, formula = W_L~WAR)
```

## Plot the Regression Fit

Create the `WL_WAR` `ggplot` object; graphs `W%` and team `bWAR` and the regression fit line.

Add layers to the ggplot by using `+` after each function/command and continuing on the next line by indenting.

```{r W_L and WAR Regression, include = TRUE, warning = FALSE, echo = TRUE, message = FALSE, render = TRUE}
  ## Create the object
WL_WAR = ggplot(data = Tot_Val_All) +
    ## Add specificity/layers (i.e. what kind of plot? dot/scatter
      ## that has WAR on X-axis, W% on Y, colored by team which will
      ## be specified later)
  geom_point(aes(x = Tot_Val_All$WAR,
                 y = Tot_Val_All$W_L,
                 color = Tot_Val_All$Tm),
             size = 4,
             alpha = 0.5) +
    ## Add the coefficient of determination using "expression" and "paste" functions within "geom_text"
  geom_text(x = 59, y = 0.7, label = expression(paste(("R")^"2", "= 0.849")), color = "black") +
    ## Provide coordinates
  coord_cartesian(xlim = c(7,68), ylim = c(0.270, 0.780)) +
    ## Make plot and axis titles
  labs(title = "MLB Team Performance Regression\n2011-2023",
       x = "Team bWAR",
       y = "W-L %",
       color = "Team") + 
    ## Override the default theme which has gray, gridded background
      ## (bw = black and white)
  theme_bw() +
      ## Provide more detail with theme parameters, including font size, grid color, etc.
  theme(plot.title = element_text(hjust = 0.5, size = 15),
        ## Remove the legend by setting position = "none"
        legend.position = "none",
        axis.ticks.x = element_blank(),
        panel.grid.major.x =  element_line(color = "gray96"),
        panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_blank(),
        axis.text = element_text(size = 10),
        axis.title = element_text(size = 13),
        axis.text.x.bottom = element_text(vjust = 1, hjust = 1)) +
      ## Go through some custom ggplot colors (links are provided at bottom of tutorial)
  scale_color_manual(values = c("darkred", "firebrick", "darkorange1", "firebrick", "dodgerblue",
                                "black", "red", "darkblue", "purple", "midnightblue",
                                "orange3", "royalblue", "firebrick1", "dodgerblue", "turquoise",
                                "goldenrod", "navy", "blue", "navyblue", "forestgreen",
                                "red", "black", "tan4", "darkorange1", "mediumseagreen",
                                "firebrick3", "navy", "blue", "deepskyblue", "red2")) +
    ## Add the regression fit line
  geom_abline(slope = as.numeric(coefficients(WL_WAR_lm)[2]),
              intercept = as.numeric(coefficients(WL_WAR_lm)[1]),
              color = "black",
              size = 1,
              linetype = "dashed")

## Plot it
WL_WAR
```

## Scrape Current Data

Scrape current `BBRef` team `WAR` data.

```{r Scrape Current WAR data, include = TRUE, echo = TRUE, message = FALSE, warning = FALSE}
  ## Hitters
BatValNew = read_html("https://www.baseball-reference.com/leagues/majors/2023-value-batting.shtml") %>%
  html_node('#teams_value_batting') %>%
  html_table() %>%
  dplyr::select(Tm, oWAR, dWAR, WAR, Salary)
  ## Remove extra rows (league avg's and spaces, etc.)
BatValNew = BatValNew[1:30,]

  ## Pitchers
PitValNew = read_html("https://www.baseball-reference.com/leagues/majors/2023-value-pitching.shtml") %>%
  html_node('#teams_value_pitching') %>%
  html_table() %>%
  dplyr::select(Tm, RAA,WAA, WAR, Salary)
PitValNew = PitValNew[1:30,]

  ## Copy the Hitters df
TotValNew = BatValNew
  ## Overwrite it with the WAR total, adding hitting bWAR and pitching bWAR
TotValNew$WAR = as.numeric(TotValNew$WAR) + as.numeric(PitValNew$WAR)
```

Scrape current `BBRef` `Standings` data and add the relevant `Standings` data to the `WAR` df.

```{r Scrape Current Standings data, include = TRUE, echo = TRUE, message = FALSE, warning = FALSE}
TotStandNew = read_html("https://www.baseball-reference.com/leagues/majors/2023-standings.shtml") %>%
  html_nodes(xpath = '//comment()') %>%
  html_text() %>%
  paste(collapse = '') %>%
  read_html() %>%
  html_node('#expanded_standings_overall') %>%
  html_table()

  ## Remove Rank column and the average row
TotStandNew = TotStandNew[-31,-1]

  ## Add Games col
TotStandNew = add_column(TotStandNew, G = TotStandNew$W + TotStandNew$L, .before = 2)
  
  ## Re-arrange the WAR and Standings dfs alphabetically
TotValNew = TotValNew %>%
  arrange(Tm)

TotStandNew = TotStandNew %>%
  arrange(Tm)

  ## Co-erce the data types to be "numeric" to enable mathematic operations
TotValNew$G = as.numeric(TotStandNew$G)
  ## Create the WAR / G variable
TotValNew$WARPG = as.numeric(TotValNew$WAR) / as.numeric(TotValNew$G)

TotValNew$W = as.numeric(TotStandNew$W)
TotValNew$W_L = as.numeric(TotStandNew$`W-L%`)
```

## Plotting

Extract team logos with the `load_mlb_teams` function and join the logos with `Standings + WAR` df.

```{r Prep the Plot data, include = TRUE, echo = TRUE, warning = FALSE, message = FALSE, render = TRUE}
  ## Make the output a variable
teams_colors_logos = load_mlb_teams() %>%
    ## Pipe the function to remove rows that don't have "AL", "NL", or "MLB" as strings
    ## in the "team_primary_abbr" column
  dplyr::filter(team_league %in% c("AL", "NL", "MLB"))

  ## Create a new variable (w_logos) by joining the Standings + WAR df with the logos variable by Tm/team_name
w_logos = TotValNew %>%
  left_join(teams_colors_logos, by = c("Tm" = "team_name"))
```

Plot the current standings data and include the regression line derived from 2011-2021 data (above), omitting 2020.

```{r Generating the ggplot Regression, include = TRUE, echo = TRUE, warning = FALSE, message = FALSE, render = TRUE}

  ## Create a ggplot object, putting WAR/G on the X-axis, and W% on the Y-axis
  
  ## I played around with width to fit it into R's plotting window
ggplot(data = w_logos, aes(x = WARPG, y = W_L), width = 0.08) +
    ## Map the logos to the variables of the ggplot object (x = WARPG, y = W_L)
      ## Map the "team_savant_abbr" to "team_primary_abbr"; not the most intuitive,
      ## but I figured it out
        ## "alpha" controls transparency
  geom_mlb_logos(aes(x = WARPG, y = W_L, team_abbr = team_abbr), alpha = 0.6, width = 0.08) +
    ## Set the X-axis and Y-axis limits (I used the min and max of each var)
  coord_cartesian(xlim = c(min(w_logos$WARPG),
                           max(w_logos$WARPG)),
                  ylim = c(min(w_logos$W_L),
                           max(w_logos$W_L))) +
    ## Set the Plot title, and X/Y axis titles
  labs(title = "MLB Win % bWAR/G in 2023 Reg. Season",
       x = "bWAR/G",
       y = "Win %",
       color = "Team") + 
    ## theme_bw will give a black/white background, removing the default gray and lines
  theme_bw() +
    ## Control the text details of the plot
  theme(plot.title = element_text(hjust = 0.5, size = 15),
        ## when "legend.position" = "none", there is no legend (title and text were copied)
        ## from another graph and included for reference
        legend.position = "none",
        legend.title = element_text(size = 13),
        legend.text = element_text(size = 11),
        ## "element_blank()" makes whatever aesthetic not have lines or text, etc.
        axis.ticks.x = element_blank(),
        panel.grid.major.x =  element_line(color = "gray96"),
        panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_blank(),
        axis.text = element_text(size = 10),
        axis.title = element_text(size = 13),
        axis.text.x.bottom = element_text(vjust = 1, hjust = 1)) +
    ## Add the regression line built from the model
  geom_abline(slope = as.numeric(coefficients(WL_WARPG_lm)[2]),
              intercept = as.numeric(coefficients(WL_WARPG_lm)[1]),
              color = "black",
              size = 1,
              linetype = "dashed") +
    ## Fiddle around with where to put the text that labels the regression line
  geom_text(x = 0.10, y = 0.41, label = "Expected\nWin %", color = "black")
```

Just a couple of the most useful R links out there:
[ggplot color link](https://www.datanovia.com/en/blog/awesome-list-of-657-r-color-names/), [ggplot cheatsheet link](https://nyu-cdsc.github.io/learningr/assets/data-visualization-2.1.pdf), [SQL in R (aka tidyverse) link](https://nyu-cdsc.github.io/learningr/assets/data-transformation.pdf).

There are tons more of material that I've saved over years of work. Just reach out if you can't find something.