---
title: "Central Valley Strat-O-Matic League 2022 Universes and Leaderboards"
author: "Erik Larsen"
date: "2/9/2022"
output: github_document
---

This snippet cleans `FanGraphs (FG)` and `Baseball-Reference (BR)` player Leaderboards (`catchers`, `pitchers`, and `non-catchers`). When scraping, the `FG Leaderboards` do not return the full tables. The `BR Leaderboards` cannot be scraped; thus, all were downloaded as `CSV`s.  
This snippet also incorporates the `MLB` franchises from which our `Strat-O-Matic` baseball dynasty league, [The Central Valley Strat-O-Matic Baseball League (CVSL)](https://sites.google.com/view/cvslbaseball/home), can draft players.  
This snippet is based on the `R script`, [CVSL 2022 FG Universes and Leaderboards](C:/Users/Erik/Desktop/BoxCopy/Programming Scripts and Data/Baseball/CVSL/CVSL 2022 FG Universes and Leaderboards.R).

Required packages: [readr](https://cran.r-project.org/package=readr), [tidyverse](https://cran.r-project.org/package=tidyverse)

## Environment Prep

```{r Package Upload, include = TRUE, warning = FALSE, message = FALSE, echo = FALSE}
library(readr)
library(tidyverse)
```

Set the working directory and import the `FG 2021 Leaderboards` for `Hitters`, `Pitchers`, and `Catchers`.  
`CVSL` rules require  
+ `eligible pitchers` to have accrued `30 IP`  
+ `eligible non-catchers` to have accrued `175 AB`  
+ `catchers` to have accrued `100 AB`

So these criteria were applied to `FG Leaderboard` queries.

## Data import

```{r 2021 FG data import, include = TRUE, message = FALSE, warning = FALSE, echo = TRUE}
  ### FG 2021 Pitchers and Hitters totals and splits ###
files = list.files(path = "C:/Users/Erik/Desktop/BoxCopy/Strato/2022/", pattern = "2021 FG")
for ( i in 1:length(files) ) {
  as.data.frame(
    assign(
      gsub(".csv", "", files[], fixed = TRUE)[i], read.csv(file = paste("C:/Users/Erik/Desktop/BoxCopy/Strato/2022/",files[i], sep = "")))
  )
}
  ## Re-name the FG tables containing minima for splits in 2021
Hitters_total = `2021 FG Hitters min 50 PA`
Hitters_split = `2021 FG Hitters min 50 PA Split teams`
Hitters_adv = `2021 FG Adv 100 PA min`
Pitchers_total = `2021 FG Pitchers min 30 IP`
Pitchers_split = `2021 FG Pitchers min 30 IP Split teams`
Pitchers_adv_2021 = `2021 FG Adv 30 IP min`
Catchers_total = `2021 FG Catchers min 100 PA`
  ## Remove the old objects
rm(`2021 FG Hitters min 50 PA`,
   `2021 FG Hitters min 50 PA Split teams`,
   `2021 FG Pitchers min 30 IP`,
   `2021 FG Pitchers min 30 IP Split teams`,
   `2021 FG Catchers min 100 PA`,
   `2021 FG Adv 30 IP min`,
   `2021 FG Adv 100 PA min`)
```

Import `FG Hitters Advanced` Leaderboards for advanced metrics `from the last 6 seasons`.

```{r FG Hitters Advanced import, include = TRUE, message = FALSE, warning = FALSE, echo = TRUE}
  ### FG Hitters advanced metrics for each season in the league
files = list.files(path = "C:/Users/Erik/Desktop/BoxCopy/Strato/2022/", pattern = "FG Adv 100 PA min")
for ( i in 1:length(files) ) {
  as.data.frame(
    assign(
      gsub(".csv", "", files[], fixed = TRUE)[i], read.csv(file = paste("C:/Users/Erik/Desktop/BoxCopy/Strato/2022/",files[i], sep = "")))
  )
}
  ## Re-name the FG tables for hitters containing advanced metrics for each season
Hitters_adv_2016 = `2016 FG Adv 100 PA min`
Hitters_adv_2017 = `2017 FG Adv 100 PA min`
Hitters_adv_2018 = `2018 FG Adv 100 PA min`
Hitters_adv_2019 = `2019 FG Adv 100 PA min`
Hitters_adv_2020 = `2020 FG Adv 100 PA min`
Hitters_adv_2021 = `2021 FG Adv 100 PA min`
    ## delete the old objects
rm(`2016 FG Adv 100 PA min`,
   `2017 FG Adv 100 PA min`,
   `2018 FG Adv 100 PA min`,
   `2019 FG Adv 100 PA min`,
   `2020 FG Adv 100 PA min`,
   `2021 FG Adv 100 PA min`)
  ## Fix the "Name" column names
colnames(Hitters_adv_2016)[1] = "Name"
colnames(Hitters_adv_2017)[1] = "Name"
colnames(Hitters_adv_2018)[1] = "Name"
colnames(Hitters_adv_2019)[1] = "Name"
colnames(Hitters_adv_2020)[1] = "Name"
colnames(Hitters_adv_2021)[1] = "Name"
```

Import `BR Leaderboards` that contain handedness and position information. Wrangle the data into a format to manipulate.

```{r BR Leaderboard import, include = TRUE, message = FALSE, warning = FALSE, echo = TRUE}
files = list.files(path = "C:/Users/Erik/Desktop/BoxCopy/Strato/2022/", pattern = "BR")
for (i in 1:length(files) ) {
  as.data.frame(
    assign(
      gsub(".csv", "", files[], fixed = TRUE)[i], read.csv(file = paste("C:/Users/Erik/Desktop/BoxCopy/Strato/2022/",files[i], sep = ""), encoding = "UTF8")
    )
  )
}
  ## Re-name them to include underscores
    ##  First, concatenate the dataframe names into a list
BR_list = ls()[
  which(grepl(ls(), pattern = "BR") == TRUE)
]
    ## Replace the spaces with underscores and assign the files to the names
for(i in 1:length(unlist(BR_list))){
    
    BR_list[i] = gsub(" ", "_", ls()[
      which(grepl(ls(), pattern = "BR") == TRUE)[i]
    ], fixed = TRUE)
    
    as.data.frame(
      assign(unlist(BR_list)[i], read.csv(file = paste("C:/Users/Erik/Desktop/BoxCopy/Strato/2022/", files[i], sep = ""), encoding = "UTF8")
    )
    )
}
```

Create a function that cleans the `BR` data (not shown).  
The data's `encoding` is recognized as "unknown", though it is `latin-1` and co-erced into `UTF-8` upon import.  
This creates problems with strings/characters. The subsequent function largely corrects for this, along with also decoding `BR`'s position and handedness encodings.

```{r BR df clean fn, include = TRUE, message = FALSE, warning = FALSE, echo = FALSE}
clean_BR_df_fn = function(df, Player_type, Year){
  if (Player_type == "Hitter") {
    df = df[ , -c(1,3) ]
    df = add_column(df, "Bats" = "", .after = 4)
    df$Bats[which(grepl(df$Name, pattern = "\\*") == TRUE)] = "L"
    df$Name = gsub(df$Name, pattern = "\\*", replacement = "")
    df$Bats[which(grepl(df$Name, pattern = "\\#") == TRUE)] = "B"
    df$Name = gsub(df$Name, pattern = "\\#", replacement = "")
    df$Bats[which(df$Bats == "")] = "R"
    colnames(df)[3] = "Team"
    colnames(df)[ncol(df)] = "Positions"
    
    if (Year == "2016"){
        ## Remove the unrecognized characters
      df$Name = gsub(df$Name, pattern = "(?!'|-)[^[a-zA-Z,.]|]", replacement = " ", perl = TRUE)
        ## Shrink the extra spaces down
      df$Name = gsub(df$Name, pattern = "  ", replacement = " ", perl = TRUE)
        ## Remove spaces at the end of strings
      df$Name = gsub(df$Name, pattern = "\\s$", replacement = "", perl = TRUE)
        ## Add missing vowels
      df$Name[which(grepl(df$Name, pattern = "[A-Z]{1}\\s[a-z]") == TRUE)] = c("Yoenis Cespedes", "Aledmys Diaz", "Hector Olivera")
        ## Add missing vowels
      df$Name[which(grepl(df$Name, pattern = "[a-z]{1}\\s[a-z]") == TRUE)][c(1,6,7,8,9,10)] = c("Gerardo Concepcion", "Leonys Martin", "Alexei Ramirez", "Alexei Ramirez", "Alexei Ramirez", "Yasmany Tomas")
    }
    if (Year == "2017"){
      df$Name = gsub(df$Name, pattern = "(?!'|-)[^[a-zA-Z,.]|]", replacement = " ", perl = TRUE)
      df$Name = gsub(df$Name, pattern = "  ", replacement = " ", perl = TRUE)
      df$Name = gsub(df$Name, pattern = "\\s$", replacement = "", perl = TRUE)
      df$Name[which(grepl(df$Name, pattern = "[A-Z]{1}\\s[a-z]") == TRUE)] = c("Yoenis Cespedes", "Aledmys Diaz", "Yandy Diaz")
      df$Name[which(grepl(df$Name, pattern = "[a-z]{1}\\s[a-z]") == TRUE)][c(9:12)] = c("Leonys Martin", "Leonys Martin", "Leonys Martin", "Yasmany Tomas")
    }
    if (Year == "2018"){
        ## Remove the unrecognized characters
      df$Name = gsub(df$Name, pattern = "(?!'|-)[^[a-zA-Z,.]|]", replacement = " ", perl = TRUE)
        ## Shrink the extra spaces down
      df$Name = gsub(df$Name, pattern = "  ", replacement = " ", perl = TRUE)
        ## Add the missing vowels
      df$Name[which(grepl(df$Name, pattern = "[A-Z]{1}\\s[a-z]") == TRUE)] = c("Yoenis Cespedes", "Aledmys Diaz", "Yandy Diaz", "Yoan Lopez", "Cionel Perez")
        ## Add more missing vowels
      df$Name[which(grepl(df$Name, pattern = "[a-z]{1}\\s[a-z]") == TRUE)][c(5:8)] = c("Adolis Garcia", "Leonys Martin", "Leonys Martin", "Leonys Martin")
        ## Add more missing vowels
      df$Name[which(grepl(df$Name, pattern = "Jos "))] = c("Jose Abreu", "Jose Iglesias")
        ## Make sure of additional _A-Z_ are shrunk down
      df$Name = gsub(df$Name, pattern = "\\s[A-Z]{1}\\s", replacement = " ", perl = TRUE)
    }
    if (Year == "2019"){
      df$Name = gsub(df$Name, pattern = "(?!'|-)[^[a-zA-Z,.]|]", replacement = " ", perl = TRUE)
      df$Name = gsub(df$Name, pattern = "  ", replacement = " ", perl = TRUE)
      df$Name[which(grepl(df$Name, pattern = "[A-Z]{1}\\s[a-z]") == TRUE)] = c("Michel Baez", "Aledmys Diaz", "Yandy Diaz", "Yoan Lopez", "Cionel Perez")
      df$Name[which(grepl(df$Name, pattern = "[a-z]{1}\\s[a-z]") == TRUE)][c(7,8,10)] = c("Leonys Martin", "Adrian Morejon", "Yasmany Tomas")
      df$Name[which(grepl(df$Name, pattern = "Jos "))] = c("Jose Abreu", "Jose Iglesias")
      df$Name[which(grepl(df$Name, pattern = "Yordan"))] = "Yordan Alvarez"
      df$Name = gsub(df$Name, pattern = "\\s[A-Z]{1}\\s", replacement = " ", perl = TRUE)
    }
    if (Year == "2020"){
      df$Name = gsub(df$Name, pattern = "(?!'|-)[^[a-zA-Z,.]|]", replacement = " ", perl = TRUE)
      df$Name = gsub(df$Name, pattern = "  ", replacement = " ", perl = TRUE)
      df$Name = gsub(df$Name, pattern = "\\s$", replacement = "", perl = TRUE)
      df$Name[which(grepl(df$Name, pattern = "[A-Z]{1}\\s[a-z]") == TRUE)] = c("Yoenis Cespedes", "Aledmys Diaz", "Yandy Diaz", "Jorge Ona")
      df$Name[which(grepl(df$Name, pattern = "[a-z]{1}\\s[a-z]") == TRUE)][c(2,3)] = c("Adolis Garcia", "Yadiel Hernandez")
      df$Name[which(grepl(df$Name, pattern = "Jos "))] = c("Jose Abreu", "Jose Barrero", "Jose Iglesias")
      df$Name[which(grepl(df$Name, pattern = "Yordan"))] = "Yordan Alvarez"
      df$Name = gsub(df$Name, pattern = "\\s[A-Z]{1}\\s", replacement = " ", perl = TRUE)
      
    }
    if (Year == "2021"){
      df$Name = gsub(df$Name, pattern = "(?!'|-)[^[a-zA-Z,.]|]", replacement = " ", perl = TRUE)
      df$Name = gsub(df$Name, pattern = "  ", replacement = " ", perl = TRUE)
      df$Name[which(grepl(df$Name, pattern = "[A-Z]{1}\\s[a-z]") == TRUE)] = c("Yandy Diaz", "Aledmys Diaz", "Cionel Perez", "Yoan Lopez")
      df$Name[which(grepl(df$Name, pattern = "[a-z]{1}\\s[a-z]") == TRUE)][c(4,6)] = c("Vladimir Gutierrez", "Adrian Morejon")
      df$Name[which(grepl(df$Name, pattern = "Jos "))] = c("Jose Abreu", "Jose Barrero")
      df$Name[which(grepl(df$Name, pattern = "Yordan"))] = "Yordan Alvarez"
      df$Name = gsub(df$Name, pattern = "\\s[A-Z]{1}\\s", replacement = " ", perl = TRUE)
    }
    df = df[ -c(which(grepl(df$Name, pattern = "LgAvg") == TRUE)), ]
  }
  if (Player_type == "Pitcher") {
    df = df[ , -c(1,3)]
    df = add_column(df, "Throws" = "", .after = 4)
    df$Throws[which(grepl(df$Name, pattern = "\\*") == TRUE)] = "L"
    df$Name = gsub(df$Name, pattern = "\\*", replacement = "")
    df$Throws[which(df$Throws == "")] = "R"
    colnames(df)[3] = "Team"
    
    if (Year == "2016") {
      df$Name = gsub(df$Name, pattern = "(?!'|-)[^[a-zA-Z,.]|]", replacement = " ", perl = TRUE)
      df$Name = gsub(df$Name, pattern = "  ", replacement = " ", perl = TRUE)
      df$Name = gsub(df$Name, pattern = "\\s$", replacement = "", perl = TRUE)
      df$Name[which(grepl(df$Name, pattern = "[A-Z]{1}\\s[a-z]") == TRUE)] = c("Michel Baez", "Yoan Lopez", "Cionel Perez")
      df$Name[which(grepl(df$Name, pattern = "[a-z]{1}\\s[a-z]") == TRUE)][1] = "Gerardo Concepcion"
      df$Name = gsub(df$Name, pattern = "\\s[A-Z]{1}\\s", replacement = " ", perl = TRUE)
    }
    if (Year == "2017") {
      df$Name = gsub(df$Name, pattern = "(?!'|-)[^[a-zA-Z,.]|]", replacement = " ", perl = TRUE)
      df$Name = gsub(df$Name, pattern = "  ", replacement = " ", perl = TRUE)
      df$Name = gsub(df$Name, pattern = "\\s$", replacement = "", perl = TRUE)
      df$Name[which(grepl(df$Name, pattern = "[a-z]{1}\\s[a-z]") == TRUE)][c(2,3)] = c("Onelki Garcia", "Leonys Martin")
      df$Name = gsub(df$Name, pattern = "\\s[A-Z]{1}\\s", replacement = " ", perl = TRUE)
    }
    if (Year == "2018") {
      df$Name = gsub(df$Name, pattern = "(?!'|-)[^[a-zA-Z,.]|]", replacement = " ", perl = TRUE)
      df$Name = gsub(df$Name, pattern = "  ", replacement = " ", perl = TRUE)
      df$Name = gsub(df$Name, pattern = "\\s$", replacement = "", perl = TRUE)
      df$Name[which(grepl(df$Name, pattern = "[A-Z]{1}\\s[a-z]") == TRUE)] = c("Yoan Lopez", "Cionel Perez")
      df$Name = gsub(df$Name, pattern = "\\s[A-Z]{1}\\s", replacement = " ", perl = TRUE)
    }
    if (Year == "2019") {
      df$Name = gsub(df$Name, pattern = "(?!'|-)[^[a-zA-Z,.]|]", replacement = " ", perl = TRUE)
      df$Name = gsub(df$Name, pattern = "  ", replacement = " ", perl = TRUE)
      df$Name = gsub(df$Name, pattern = "\\s$", replacement = "", perl = TRUE)
      df$Name[which(grepl(df$Name, pattern = "[A-Z]{1}\\s[a-z]") == TRUE)] = c("Michel Baez", "Yoan Lopez", "Cionel Perez")
      df$Name[which(grepl(df$Name, pattern = "[a-z]{1}\\s[a-z]") == TRUE)][c(2,4)] = c("Adrian Morejon", "Jose Rodriguez")
      df$Name = gsub(df$Name, pattern = "\\s[A-Z]{1}\\s", replacement = " ", perl = TRUE)
    }
    if (Year == "2020") {
      df$Name = gsub(df$Name, pattern = "(?!'|-)[^[a-zA-Z,.]|]", replacement = " ", perl = TRUE)
      df$Name = gsub(df$Name, pattern = "  ", replacement = " ", perl = TRUE)
      df$Name = gsub(df$Name, pattern = "\\s$", replacement = "", perl = TRUE)
      df$Name[which(grepl(df$Name, pattern = "[A-Z]{1}\\s[a-z]") == TRUE)] = c("Michel Baez", "Yoan Lopez", "Cionel Perez")
      df$Name[which(grepl(df$Name, pattern = "[a-z]{1}\\s[a-z]") == TRUE)][c(2,4)] = c("Adrian Morejon", "Jose Rodriguez")
      df$Name = gsub(df$Name, pattern = "\\s[A-Z]{1}\\s", replacement = " ", perl = TRUE)
    }
    if (Year == "2021") {
      df$Name = gsub(df$Name, pattern = "(?!'|-)[^[a-zA-Z,.]|]", replacement = " ", perl = TRUE)
      df$Name = gsub(df$Name, pattern = "  ", replacement = " ", perl = TRUE)
      df$Name = gsub(df$Name, pattern = "\\s$", replacement = "", perl = TRUE)
      df$Name[which(grepl(df$Name, pattern = "[A-Z]{1}\\s[a-z]") == TRUE)] = c("Yoan Lopez", "Cionel Perez")
      df$Name[which(grepl(df$Name, pattern = "[a-z]{1}\\s[a-z]") == TRUE)][c(5,6)] = c("Vladimir Gutierrez", "Adrian Morejon")
      df$Name = gsub(df$Name, pattern = "\\s[A-Z]{1}\\s", replacement = " ", perl = TRUE)
    }
    df = df[ -c(which(grepl(df$Name, pattern = "LgAvg") == TRUE)), ]
  }
  return(df)
}
  ## Delete the old dfs with spaces
rm(`BR 2016 Standard Batting Leaders`, `BR 2016 Standard Pitching Leaders`,
   `BR 2017 Standard Batting Leaders`, `BR 2017 Standard Pitching Leaders`,
   `BR 2018 Standard Batting Leaders`, `BR 2018 Standard Pitching Leaders`,
   `BR 2019 Standard Batting Leaders`, `BR 2019 Standard Pitching Leaders`,
   `BR 2020 Standard Batting Leaders`, `BR 2020 Standard Pitching Leaders`,
   `BR 2021 Standard Batting Leaders`, `BR 2021 Standard Pitching Leaders`,
   BR_list)
```
Call all the `BR` data into the newly-created function.
```{r Clean BR data, include = TRUE, message = FALSE, warning = FALSE, echo = TRUE}
  ## Clean the dfs; remove unrecognized characters due to improper encoding,
    ##  remove extra columns and rows; re-name strings, convert handedness
BR_2016_Standard_Pitching_Leaders = clean_BR_df_fn(df = BR_2016_Standard_Pitching_Leaders, Player_type = "Pitcher", Year = "2016")
BR_2017_Standard_Pitching_Leaders = clean_BR_df_fn(df = BR_2017_Standard_Pitching_Leaders, Player_type = "Pitcher", Year = "2017")
BR_2018_Standard_Pitching_Leaders = clean_BR_df_fn(df = BR_2018_Standard_Pitching_Leaders, Player_type = "Pitcher", Year = "2018")
BR_2019_Standard_Pitching_Leaders = clean_BR_df_fn(df = BR_2019_Standard_Pitching_Leaders, Player_type = "Pitcher", Year = "2019")
BR_2020_Standard_Pitching_Leaders = clean_BR_df_fn(df = BR_2020_Standard_Pitching_Leaders, Player_type = "Pitcher", Year = "2020")
BR_2021_Standard_Pitching_Leaders = clean_BR_df_fn(df = BR_2021_Standard_Pitching_Leaders, Player_type = "Pitcher", Year = "2021")

BR_2016_Standard_Pitching_Leaders = BR_2016_Standard_Pitching_Leaders[ -which(duplicated(BR_2016_Standard_Pitching_Leaders$Name)), ]
BR_2017_Standard_Pitching_Leaders = BR_2017_Standard_Pitching_Leaders[ -which(duplicated(BR_2017_Standard_Pitching_Leaders$Name)), ]
BR_2018_Standard_Pitching_Leaders = BR_2018_Standard_Pitching_Leaders[ -which(duplicated(BR_2018_Standard_Pitching_Leaders$Name)), ]
BR_2019_Standard_Pitching_Leaders = BR_2019_Standard_Pitching_Leaders[ -which(duplicated(BR_2019_Standard_Pitching_Leaders$Name)), ]
BR_2020_Standard_Pitching_Leaders = BR_2020_Standard_Pitching_Leaders[ -which(duplicated(BR_2020_Standard_Pitching_Leaders$Name)), ]
BR_2021_Standard_Pitching_Leaders = BR_2021_Standard_Pitching_Leaders[ -which(duplicated(BR_2021_Standard_Pitching_Leaders$Name)), ]

BR_2016_Standard_Batting_Leaders = clean_BR_df_fn(df = BR_2016_Standard_Batting_Leaders, Player_type = "Hitter", Year = "2016")
BR_2017_Standard_Batting_Leaders = clean_BR_df_fn(df = BR_2017_Standard_Batting_Leaders, Player_type = "Hitter", Year = "2017")
BR_2018_Standard_Batting_Leaders = clean_BR_df_fn(df = BR_2018_Standard_Batting_Leaders, Player_type = "Hitter", Year = "2018")
BR_2019_Standard_Batting_Leaders = clean_BR_df_fn(df = BR_2019_Standard_Batting_Leaders, Player_type = "Hitter", Year = "2019")
BR_2020_Standard_Batting_Leaders = clean_BR_df_fn(df = BR_2020_Standard_Batting_Leaders, Player_type = "Hitter", Year = "2020")
BR_2021_Standard_Batting_Leaders = clean_BR_df_fn(df = BR_2021_Standard_Batting_Leaders, Player_type = "Hitter", Year = "2021")

  ## Check that strings are compatible to merge BR info with FG info
BR_2021_Standard_Batting_Leaders$Name[which(grepl(BR_2021_Standard_Batting_Leaders$Name, pattern = "Whit Merrifield") == TRUE)]
BR_2021_Standard_Pitching_Leaders$Name[grepl(BR_2021_Standard_Pitching_Leaders$Name, pattern = "\\s")][c(1:10)]
```

```{r include = FALSE, message = FALSE, warning = FALSE, echo = FALSE}
library(rvest)
library(XML)
  ##### FanGraphs pitcher leaderboards scraped from FG #####
  ## Import the advanced pitching metric dfs scraped from FGs from 2019 and 2020 (2021 already included)
FG_selector = "#LeaderBoard1_dg1_ctl00 > tbody"
FG_col_selector = "#LeaderBoard1_dg1_ctl00 > thead > tr:nth-child(2)"
FG_  = "#LeaderBoard1_dg1_ctl00"


  ## Scrape the table that includes the column names
Pitchers_adv_2019 = read_html("https://www.fangraphs.com/leaders.aspx?pos=all&stats=pit&lg=all&qual=30&type=1&season=2021&month=0&season1=2019&ind=0&team=0&rost=0&age=0&filter=&players=0&startdate=2019-01-01&enddate=2019-12-31") %>%
  html_element(css = FG_) %>%
  html_table()
  ## slice to create a vector of column names
col_names = Pitchers_adv_2019[2,]

  ## Scrape the data, overwriting the old table that doesn't have the column names
Pitchers_adv_2019 = read_html("https://www.fangraphs.com/leaders.aspx?pos=all&stats=pit&lg=all&qual=30&type=1&season=2021&month=0&season1=2019&ind=0&team=0&rost=0&age=0&filter=&players=0&startdate=2019-01-01&enddate=2019-12-31") %>%
  html_element(css = FG_selector) %>%
  html_table()
  ## Re-name the columns
colnames(Pitchers_adv_2019) = col_names

Pitchers_adv_2020 = read_html("https://www.fangraphs.com/leaders.aspx?pos=all&stats=pit&lg=all&qual=30&type=1&season=2021&month=0&season1=2020&ind=0&team=0&rost=0&age=0&filter=&players=0&startdate=2020-01-01&enddate=2020-12-31") %>%
  html_element(css = FG_selector) %>%
  html_table()
  ## Re-name the columns
colnames(Pitchers_adv_2020) = col_names

Pitchers_adv_2018 = read_html("https://www.fangraphs.com/leaders.aspx?pos=all&stats=pit&lg=all&qual=30&type=1&season=2018&month=0&season1=2018&ind=0&team=0&rost=0&age=0&filter=&players=0&startdate=2018-01-01&enddate=2018-12-31") %>%
  html_element(css = FG_selector) %>%
  html_table()
## Re-name the columns
colnames(Pitchers_adv_2018) = col_names

  ## Remove the "rank column"
Pitchers_adv_2018 = Pitchers_adv_2018[,-1]
Pitchers_adv_2019 = Pitchers_adv_2019[,-1]
Pitchers_adv_2020 = Pitchers_adv_2020[,-1]
```

Import the `FG` `Pitcher Leaderboards`.

```{r FG P Leaderboards import, include = TRUE, message = FALSE, warning = FALSE, echo = TRUE}
  ## FanGraphs pitcher leaderboards downloads
files = list.files(path = "C:/Users/Erik/Desktop/BoxCopy/Strato/2022/", pattern = "FG Pitchers min 30 IP")
for ( i in 1:length(files) ) {
  as.data.frame(
    assign(
      gsub(".csv", "", files[], fixed = TRUE)[i], read.csv(file = paste("C:/Users/Erik/Desktop/BoxCopy/Strato/2022/",files[i], sep = "")))
  )
}
Pitchers_2016 = `2016 FG Pitchers min 30 IP`
Pitchers_2017 = `2017 FG Pitchers min 30 IP`
Pitchers_2018 = `2018 FG Pitchers min 30 IP`
Pitchers_2019 = `2019 FG Pitchers min 30 IP`
Pitchers_2020 = `2020 FG Pitchers min 30 IP`
Pitchers_2021 = `2021 FG Pitchers min 30 IP`
rm(`2016 FG Pitchers min 30 IP`,
   `2017 FG Pitchers min 30 IP`,
   `2018 FG Pitchers min 30 IP`,
   `2019 FG Pitchers min 30 IP`,
   `2020 FG Pitchers min 30 IP`,
   `2021 FG Pitchers min 30 IP`,
   `2021 FG Pitchers min 30 IP Split teams`)
  ## Re-name all the other FG df "Name" columns;
colnames(Pitchers_2016)[1] = "Name"
colnames(Pitchers_2017)[1] = "Name"
colnames(Pitchers_2018)[1] = "Name"
colnames(Pitchers_2019)[1] = "Name"
colnames(Pitchers_2020)[1] = "Name"
colnames(Pitchers_2021)[1] = "Name"

  ## Re-name all the other FG df "Name" columns; these are all dfs of stats from 2021
colnames(Hitters_total)[1] = "Name"
colnames(Hitters_split)[1] = "Name"
colnames(Hitters_adv)[1] = "Name"
colnames(Pitchers_total)[1] = "Name"
colnames(Pitchers_split)[1] = "Name"
colnames(Pitchers_adv_2021)[1] = "Name"
colnames(Catchers_total)[1] = "Name"

  ## Create a function that enables to pipe an object's strings through another object's strings
"%notin%" = Negate("%in%")
```

## Establish "Universes"

The "`CVSL Universe`" consists of the following teams:

```{r include = TRUE, message = FALSE, warning = FALSE, echo = TRUE}
CVSL_universe = c("LAA", "OAK", "TEX", "SFG", "COL",
                  "LAD", "SDP", "ARI", "MIN", "CLE",
                  "STL", "NYY", "BOS", "TOR", "TBR",
                  "NYM", "PHI", "ATL", "MIA", "WSN")
```

Process the `FG` `Hitters_total` df to include **only hitters with >= 100 ABs**

```{r include = TRUE, message = FALSE, warning = FALSE, echo = TRUE}
  ## Remove hitters with < 100 ABs
Hitters_total = Hitters_total[ which(Hitters_total$AB >= 100), ]
rownames(Hitters_total) = NULL
  ## Confirm pitchers are not included in the df (should only be Shohei Ohtani)
Hitters_total$Name[ which(Hitters_total$playerid %in% Pitchers_total$playerid) ]
```

Find which hitters changed teams.

```{r include = TRUE, message = FALSE, warning = FALSE, echo = TRUE}
  ## Find which hitters changed teams
dashed_hitters = Hitters_total$Name[ which( Hitters_total$Team == "- - -") ]
  ## Iterate through to subset the split df
    ## by those that have been traded and accrued >= 100 ABs
dummy = vector()
for ( i in 1:length(dashed_hitters) ){
  dummy[i] = list(which(Hitters_split$Name == dashed_hitters[i]))
}
Traded_hitters = Hitters_split[ unlist(dummy), ]
rm(dummy)
#Traded_hitters
dashed_hitters
```

Manually curate a list of the teams to which these hitters went.  
Convert the dashes in the `Hitters_total` df to these team names.  

```{r include = TRUE, message = FALSE, warning = FALSE, echo = TRUE}
dashed_hitters_to = c("LAD", "CHC", "OAK", "SDP", "OAK",
                      "CLE", "BOS", "TOR", "BOS", "TBR",
                      "SFG", "NYM", "MIL", "ATL", "MIL",
                      "OAK", "NYY", "PIT", "BAL", "PIT",
                      "MIL", "PHI", "SEA", "ATL", "LAD",
                      "WSN", "PIT", "BAL", "CHW", "CIN",
                      "ATL", "ATL", "LAA", "PIT", "SDP",
                      "SEA", "MIA", "TOR", "OAK", "CLE",
                      "TBR", "LAA", "BOS", "HOU", "NYY",
                      "TEX", "PIT", "ATL", "TOR", "LAD",
                      "SFG", "NYY", "COL", "PIT", "MIA")

dummy = vector()

for (i in dashed_hitters){
    dummy[i] = which(Hitters_total$Name == i)
}
for (i in 1:length(dashed_hitters_to)){
    Hitters_total$Team[dummy[i]] = dashed_hitters_to[i]
}
rm(dummy)
```

Slice eligible catchers.

```{r include = TRUE, message = FALSE, warning = FALSE, echo = TRUE}
  ## Slice eligible catchers ( >= 100 ABs)
Catchers_total = Catchers_total[ which(Catchers_total$AB >= 100), ]
  ## Concatenate eligible catchers into a list
eligible_Catchers = Catchers_total$Name
```

Concatenate and slice all eligible hitters/catchers.

```{r include = TRUE, message = FALSE, warning = FALSE, echo = TRUE}
  ## Concatenate eligible hitters ( >= 175 ABs, or catchers with >= 100 ABs) into a list
eligible_Hitters = Hitters_total$Name[ which(Hitters_total$AB >= 175 | Hitters_total$Name %in% eligible_Catchers) ]

  ## Slice all eligible hitters
Hitters_total = Hitters_total[ which(Hitters_total$Name %in% eligible_Hitters) , ]
```

Find which pitchers changed teams.

```{r include = TRUE, message = FALSE, warning = FALSE, echo = TRUE}
  ## Find which pitchers changed teams
dashed_pitchers = Pitchers_total$Name[ which( Pitchers_total$Team == "- - -") ]

  ## Iterate through to subset the split data frame by those that have been traded and accrued >= 30 IP
dummy = vector()
for ( i in 1:length(dashed_pitchers) ){
  dummy[i] = list(which(Pitchers_split$Name == dashed_pitchers[i]))
}
Traded_pitchers = Pitchers_split[ unlist(dummy), ]
rm(dummy)
#Traded_pitchers
dashed_pitchers
```

Manually curate a list of the teams to which these pitchers went.  
Convert the dashes in the `Pitchers_total` df to these team names.

```{r include = TRUE, message = FALSE, warning = FALSE, echo = TRUE}
dashed_pitchers_to = c("LAD", "TOR", "PHI", "CHW", "SEA",
                       "NYM", "CHW", "TBR", "OAK", "NYM",
                       "TOR", "TBR", "HOU", "NYY", "SDP",
                       "NYY", "CIN", "SFG", "ATL", "CHC",
                       "SEA", "HOU", "NYY", "ARI", "STL",
                       "MIN", "KCR", "LAD", "HOU", "HOU",
                       "KCR", "SEA", "SEA", "MIL", "TEX",
                       "SFG", "TBR", "NYM", "TOR", "TBR",
                       "MIL", "ARI", "NYY", "SFG", "CIN",
                       "BOS", "TOR", "PIT", "SEA", "TEX",
                       "PHI", "STL", "STL", "WSN", "MIL",
                       "COL", "NYM", "PIT", "MIN", "PIT",
                       "MIA", "CIN", "SDP", "SDP", "TBR",
                       "ARI", "SDP", "CLE")
dummy = vector()

for (i in dashed_pitchers){
  dummy[i] = which(Pitchers_total$Name == i)
}
for (i in 1:length(dashed_pitchers_to)){
  Pitchers_total$Team[dummy[i]] = dashed_pitchers_to[i]
}
rm(dummy)
```

Slice all eligible `P`s within the `Pitchers_total` df.  
Concatenate all eligible `SP`s from this df into a list, `eligible_SPs`.  
Concatenate all eligible `RP`s from the same `Pitchers_total` df into a list, `eligible_RPs`.

```{r include = TRUE, message = FALSE, warning = FALSE, echo = TRUE}
  ## Slice eligible pitchers
Pitchers_total = Pitchers_total[ which(Pitchers_total$IP >= 30), ]

  ## Concatenate eligible starters into a list
eligible_SPs = Pitchers_total$Name[ which(Pitchers_total$IP >= 30 & Pitchers_total$GS >= 8) ]
  ## Concatenate eligible relievers into a list
eligible_RPs = Pitchers_total$Name[ which(Pitchers_total$Name %notin% eligible_SPs == TRUE) ]
```

Filter the lists by the `CVSL_universe`.

```{r include = TRUE, message = FALSE, warning = FALSE, echo = TRUE}
  ## Find eligible catchers that are outside the CVSL universe
Hitters_total$Name[ which( Hitters_total$Name %in% eligible_Catchers == TRUE )[
  which(
    Hitters_total$Team[ which( Hitters_total$Name %in% eligible_Catchers == TRUE ) ] %notin% CVSL_universe == TRUE
  )
]
]
eligible_Catchers_out = Hitters_total$Name[ which( Hitters_total$Name %in% eligible_Catchers == TRUE )[
  which(
    Hitters_total$Team[ which( Hitters_total$Name %in% eligible_Catchers == TRUE ) ] %notin% CVSL_universe == TRUE
  )
]
]

  ## Find eligible hitters that are outside the CVSL universe
Hitters_total$Name[ which( Hitters_total$Name %in% eligible_Hitters == TRUE )[
  which(
    Hitters_total$Team[ which( Hitters_total$Name %in% eligible_Hitters == TRUE ) ] %notin% CVSL_universe == TRUE
  )
]
][c(1:15)]
eligible_Hitters_out = Hitters_total$Name[ which( Hitters_total$Name %in% eligible_Hitters == TRUE )[
  which(
    Hitters_total$Team[ which( Hitters_total$Name %in% eligible_Hitters == TRUE ) ] %notin% CVSL_universe == TRUE
  )
]
]

  ## Find eligible starting pitchers that are outside the CVSL universe
Pitchers_total$Name[ which( Pitchers_total$Name %in% eligible_SPs == TRUE )[
  which(
    Pitchers_total$Team[ which( Pitchers_total$Name %in% eligible_SPs == TRUE ) ] %notin% CVSL_universe == TRUE
  )
]
]
eligible_SPs_out = Pitchers_total$Name[ which( Pitchers_total$Name %in% eligible_SPs == TRUE )[
  which(
    Pitchers_total$Team[ which( Pitchers_total$Name %in% eligible_SPs == TRUE ) ] %notin% CVSL_universe == TRUE
  )
]
]

  ## Find eligible relievers that are outside the CVSL universe
Pitchers_total$Name[ which( Pitchers_total$Name %in% eligible_RPs == TRUE )[
  which(
    Pitchers_total$Team[ which( Pitchers_total$Name %in% eligible_RPs == TRUE ) ] %notin% CVSL_universe == TRUE
  )
]
][c(1:15)]
eligible_RPs_out = Pitchers_total$Name[ which( Pitchers_total$Name %in% eligible_RPs == TRUE )[
  which(
    Pitchers_total$Team[ which( Pitchers_total$Name %in% eligible_RPs == TRUE ) ] %notin% CVSL_universe == TRUE
  )
]
]

eligible_Ps = c(eligible_SPs, eligible_RPs)
```
